A data-intensive assessment of the species-abundance distribution.

### 2015-04-02 defense_pres.tex
Fixes data table.

\subsubsection{Data}
\begin{frame}[shrink=35]
\frametitle{SAD Comparisons}
\begin{center}
\begin{table}
\begin{tabular}{l|c|l|r}
 Dataset &Dataset code &Availability &Total sites\\
\hline
 Breeding Bird Survey &BBS &Public &2769\\
 Christmas Bird Count &CBC &Private &1999\\
 Gentry's Forest Transects &Gentry &Public &10355\\
 Forest Inventory Analysis &FIA	 &Public &220\\
 Mammal Community Database &MCDB &Public &103\\
 N. American Butterfly Count &NABA &Private &400\\
 Actinopterygii, this dissertation	 &Actinopterygii &Public &161\\
 Reptilia, this dissertation &Reptilia &Public &138\\
 Amphibia, this dissertation &Amphibia &Public &43\\
 Coleoptera, this dissertation &Coleoptera &Public &5\\
 Arachnida, this dissertation &Arachnida &Public &25\\
\end{tabular}
\caption{Datasets used for species-abundance distribution comparisons. Datasets marked as Private were obtained through data requests to the providers resulting in Memorandums of Understanding governing data use.}
\end{table}
\end{center}
\end{frame}

>>>>

\subsubsection{Data}
\begin{frame}[shrink=35]
\frametitle{SAD Comparisons}
\begin{center}
\begin{table}
\begin{tabular}{l|c|l|r}
 Dataset &Dataset code &Availability &Sites\\
\hline
 Gentry's Forest Transects &Gentry &Public &10355\\
 Breeding Bird Survey &BBS &Public &2769\\
 Christmas Bird Count &CBC &Private &1999\\
 Forest Inventory Analysis &FIA	 &Public &220\\
 N. American Butterfly Count &NABA &Private &400\\
 Actinopterygii, compiled &Actinopterygii &Public &161\\
 Reptilia, compiled &Reptilia &Public &138\\
 Mammal Community Database &MCDB &Public &103\\
 Amphibia, compiled &Amphibia &Public &43\\
 Arachnida, compiled &Arachnida &Public &25\\
 Coleoptera, compiled &Coleoptera &Public &5\\
\end{tabular}
\caption{Datasets used for species-abundance distribution comparisons. Datasets marked as Private obtained through data requests to the providers with Memorandums of Understanding.}
\end{table}
\end{center}
\end{frame}
